Multireference alignment meets blind deconvolution

### 2017-11-03 TEX/draft2.tex
New note  + update the EM code (still doesn't work)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
%\numberwithin{equation}{section}
%\numberwithin{figure}{section}
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}[section]
\theoremstyle{definition}
\newtheorem{defn}[thm]{\protect\definitionname}
\theoremstyle{remark}
\newtheorem{claim}[thm]{\protect\claimname}
\theoremstyle{plain}
\newtheorem{lem}[thm]{\protect\lemmaname}

@@

\title{Small MRI is boring}

\author{Tamir Bendory}
\maketitle

We consider the problem of estimating a signal $x\in\RL$ from one measurement $y\in\RN, \thinspace N\gg L,$ that contains many repetitions of this signal, at unknown locations, swallowed in noise.

Formally, our model read
\begin{equation}
y[n] = \sum_{i=1}^K \xz [n-n_i] + \varepsilon[n], 
\end{equation}
where:
\begin{itemize}
	\item $y\in\RN$ is the noisy acquired data (measurement),
	\item $\xz\in\RN$ is a zero-padded version of $x\in\RL, \thinspace L\ll N,
	$ defined as $\xz  = [x, \underbrace{0,0,\ldots,0}_{N-L \text{ zeros}}]$,
	\item $n_i,\quad i=1,\ldots,K,$ are the translations of $\xz$, 
	\item  $\varepsilon$ is i.i.d.\ normal noise with mean zero and variance $\sigma^2$ .
\end{itemize}

Note that both $x$ and the translations $n_i$ are unknown. Therefore, essentially, this is a blind deconvolution problem. Particularly, let $s\in\{0,1\}^N$ be the ``support" signal, which takes the value 1 at the locations $n_i$ are zero otherwise. 
Then, 
\begin{equation}
y = \xz \ast s + \varepsilon,
\end{equation}
and the goal is then to estimate $x$ from $y$ although $s$ is unknown as well.

@@

@@

@@

Few insights from the analysis: (need to check numerically)
\begin{itemize}
	\item Larger $S$ reduces the clutter error, however, increases the variance of the noise estimation.
	\item Larger $W/L$ reduces the clutter error, however, increases the variance of the noise  of $B_\textrm{noise}$.
	\item We must keep $W/L$ large enough to see enough full signals.    
\end{itemize} 
%\bibliographystyle{plain}
%\bibliography{ref}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\numberwithin{equation}{section}
\numberwithin{figure}{section}
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}[section]
\theoremstyle{definition}
\newtheorem{defn}[thm]{\protect\definitionname}
\theoremstyle{remark}
\newtheorem{claim}[thm]{\protect\claimname}
\theoremstyle{plain}
\newtheorem{lem}[thm]{\protect\lemmaname}

@@

\title{Multireference alignment meets blind deconvolution}
\author{Tamir Bendory}
\maketitle

\begin{abstract}
	Here comes the abstract
\end{abstract}

\section{Introduction} \label{sec:introduction}

Blind deconvolution is the problem of estimating a signal from its convolution with an unknown kernel. This problem arises in many engineering and scientific applications, such as astronomy, communication, deblurring and optics; see   \cite{jefferies1993restoration,tong1994blind,chan1998total,campisi2016blind,kundur1996blind,levin2011understanding,shalvi1990new,levin2009understanding,krishnan2011blind,ayers1988iterative,michaeli2014blind} to name a few.

Without prior information the blind deconvolution is clearly ill-posed. In this note, we consider a special case of the problem. We aim at estimating a signal $x\in\RL$ from $y\in\RN, \thinspace N\gg L$. The acquired data, the measurement $y$, is composed of many repetitions of $x$, at different positions, and i.i.d.\ normal noise $\varepsilon $with mean zero and variance $\sigma^2$. 
Formally, our model read
\begin{equation}
y[n] = \sum_{i=1}^K \xz [n-n_i] + \varepsilon[n], 
\end{equation}
where $\xz\in\RN$ is a zero-padded version of $x\in\RL$ and 
defined as $$\xz  = [x, \underbrace{0,0,\ldots,0}_{N-L \text{ zeros}}],$$ and
 $n_i,\quad i=1,\ldots,K,$ are the translations of $\xz$.

Note that both $x$ and the translations, or positions, $n_i$ are unknown. Let $s\in\{0,1\}^N$ be the ``support" signal, which takes the value 1 at the locations $n_i$ are zero otherwise. 
Then, 
\begin{equation}
y = \xz \ast s + \varepsilon.
\end{equation}
The goal is then to estimate $x$ from $y$, while $s$ is unknown as well. The support signal $s$ is the latent or hidden variable of the problem. This is quite common in blind deconvolution problem. For instance, in image deblurring, the both the blurring kernel and the high-resolution image are unknown, but the main goal is merely to sharpen the image.

Recent papers on blind deconvolution and deconvolution.

@@

\section{Literature survey} \label{sec:literature}

\section{Connection with the cryo--EM problem} \label{sec:cryoEM}
particle picking

\section{Algorithm} \label{sec:algorithm}

@@

\section{Analysis} \label{sec:analysis}

@@

Few insights from the analysis: (need to check numerically)
\begin{itemize}
	\item Larger $S$ reduces the clutter error, however, increases the variance of the noise estimation.
	\item Larger $W/L$ reduces the clutter error, however, increases the variance of the noise  of $B_\textrm{noise}$.
	\item We must keep $W/L$ large enough to see enough full signals.    
\end{itemize}

\section{Conclusion} \label{sec:conclusion}

\bibliographystyle{plain}
\bibliography{ref}
